---
title: "Hands on!"
author: "Beatriz Milz"
---

```{r}
#| echo: false
yaml_file_as_code <- function(file){
  code <- readLines(file) |> 
  paste0(collapse = "\n")

paste0(
  '<div class="sourceCode">
  <pre class="downlit sourceCode r code-with-copy">
  <code class="sourceCode R">',
  code,
  '</code></pre></div>'
) |> cat()
}

r_file_as_code <- function(file){
  code <- readLines(file) |> 
  paste0(collapse = "\n")

paste0(
  '<div class="sourceCode">
<pre class="downlit sourceCode r code-with-copy">
<code class="sourceCode R">
',
  code,
  '</code></pre></div>'
) |> 
  cat()
}
```

## Exploring jobs!

### 1 - Writing a simple workflow


#### `01-hello-gha.yml`


```{r}
#| results: asis
#| echo: false
#| warning: false
yaml_file_as_code(".github/workflows/01-hello-gha.yml")
```

### 2 - Print message using R!

#### `02-hello-r-world.yml`

```{r}
#| results: asis
#| echo: false
#| warning: false
yaml_file_as_code(".github/workflows/02-hello-r-world.yml")
```

### 3 - Run code from R script (only base packages)


#### `03-run-r-script.yml`

```{r}
#| results: asis
#| echo: false
#| warning: false
yaml_file_as_code(".github/workflows/03-run-r-script.yml")
```


#### `scripts/03-r-script.R`

```{r}
#| results: asis
#| echo: false
#| warning: false
r_file_as_code("scripts/03-r-script.R")
```


### 4 - Run code using other packages


#### `04-run-r-script-with-pkgs.yml`

```{r}
#| results: asis
#| echo: false
#| warning: false
yaml_file_as_code(".github/workflows/04-run-r-script-with-pkgs.yml")
```


#### `scripts/04-r-script.R`

```{r}
#| results: asis
#| echo: false
#| warning: false
r_file_as_code("scripts/04-r-script.R")
```


### 5 - Save results from code in the repository


#### `05-saving-results.yml`

```{r}
#| results: asis
#| echo: false
#| warning: false
yaml_file_as_code(".github/workflows/05-saving-results.yml")
```

## Exploring events!

### 6 - Schedule

Tip: [CronTab Guru](https://crontab.guru/).

#### `06-schedule.yml`

```{r}
#| results: asis
#| echo: false
#| warning: false
yaml_file_as_code(".github/workflows/06-schedule.yml")
```


### 7 - Changes on the code

The workflow run is triggered every time someone pushes a change to the repository or merges a pull request. 

#### `07-on-push.yml`

```{r}
#| results: asis
#| echo: false
#| warning: false
yaml_file_as_code(".github/workflows/07-on-push.yml")
```